---
title: "Retail transactions:  Monthly Report"
author: "Chloé Blanchard: Uni (chb2132)"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)
```

```{r seed}

set.seed(41)
```

```{r libraries}

library(data.table)
library(dplyr)
library(DT)
```

```{r constants}

###--------------------------------------------------------------------------###
# set working directory to show your local directory location path
###--------------------------------------------------------------------------###
setwd("~/Documents/code/5902/IP1")

###--------------------------------------------------------------------------###
# current_trans_data <- Mon_trans_data
###--------------------------------------------------------------------------###
current_trans_data <- "transactions -- January 2020.csv"

###--------------------------------------------------------------------------###
# current_view_data <- Mon_views_data
###--------------------------------------------------------------------------###
current_view_data <- "views -- January 2020.csv"

###--------------------------------------------------------------------------###
# "YEAR" <- YYYY
###--------------------------------------------------------------------------###
year <- "2020";

###--------------------------------------------------------------------------###
# "MONTH" <- Month
###--------------------------------------------------------------------------###
month <- "January";

###--------------------------------------------------------------------------###
# w1 <- YYYY-MM-09
###--------------------------------------------------------------------------###
w1 <- 2020-01-09;

customer_data <- if (file.exists("customers.csv")){
            "customers.csv"
} else{
            return('Please ensure you have the customers dataset saved to your 
                   working directory as "customers.csv", thanks.')
}

product_data <- if (file.exists("products.csv")){
            "products.csv"
} else{
            return('Please ensure you have the products dataset saved to your 
                    working directory as "products.csv", thanks.')
}

viewing_data <- if (file.exists(current_view_data)){
        current_view_data
} else{
        return('Please ensure you have the MONTH YEAR views dataset saved to 
                your working directory as "views -- MONTH YEAR", thanks.')
}

transaction_data <- if (file.exists(current_trans_data)){
            current_trans_data
} else{
            return('Please ensure you have the MONTH YEAR transactions dataset
            saved to your working directory as "transactions -- 
            MONTH YEAR.csv", thanks.')
}

```

```{r functions}

view_counter <- function(DT = DT){
  
  x <- 1;
  cu_views <- as.data.table(unique(DT$customer_id));
  
  view_len <- length(cu_views);
  customer_views <- data.table(a = c(2, view_len), 
                    b = c("customer_id", "count"));
  
  for(x in view_len){
    cu_val <- cu_views$V1[x];
    customer_views$customer_id <- cu_val;
    customer_views$count <- nrow(DT$customer_id == cu_val)
    
    }
  
  return (customer_views);
 
}

round_numerics <- function(x, digits){
###--------------------------------------------------------------------------###
# Function written by Dave Shilane
###--------------------------------------------------------------------------###
  if (is.numeric(x)) {
    x <- round(x = x, digits = digits)
    }
  return(x)
}

mean_missing <- function(x){
###--------------------------------------------------------------------------###
# Function written by Dave Shilane
###--------------------------------------------------------------------------###
  return(mean(is.na(x)))
}

show_coef <- function(mod_lm){
###--------------------------------------------------------------------------###
# Function written by Dave Shilane
###--------------------------------------------------------------------------###
  return(data.frame(Variable = names(mod_lm$coefficients),
  Coefficient = mod_lm$coefficients, p = summary(mod_lm)$coef[,
    ncol(summary(mod_lm)$coef)]))
}

```

```{r load_data}
customers <- fread(customer_data)
products <- fread(product_data)

###--------------------------------------------------------------------------###
# Be sure to update the constants in the top of the document to reflect the
# current-most month abbreviation, as well as the name of the current data files
###--------------------------------------------------------------------------###
views <- fread(viewing_data)
trans <- fread(transaction_data)
```

```{r explore_data, eval = FALSE}
dim(customers)
str(customers)
summary(customers)
head(customers)
tail(customers)

dim(products)
str(products)
summary(products)
head(products)
tail(products)

dim(views)
str(views)
summary(views)
head(views)
tail(views)

dim(trans)
str(trans)
summary(trans)
head(trans)
tail(trans)

```


```{r clean_data}

sum(is.na(customers))
charNA_customers <- which(customers == "NA")
print(charNA_customers)

sum(is.na(products))
charNA_products <- which(products == "NA")
print(charNA_products)

sum(is.na(views))
charNA_views <- which(views == "NA")
str
print(charNA_views)

sum(is.na(trans))
charNA_trans <- which(trans[,1:4] == "NA")

str(trans)
print(charNA_trans)

missingNo_customers <- customers[ , lapply(X = .SD, FUN = "mean_missing")]
missingNo_products <- products[ , lapply(X = .SD, FUN = "mean_missing")]

missingNo_views <- views[ , lapply(X = .SD, FUN = "mean_missing")]
missingNo_trans <- trans[ , lapply(X = .SD, FUN = "mean_missing")]

colnames(customers)

colnames(products)
products <- products[ , c(2, 1, 3)]

colnames(views)
views <- views[ , c(3, 1, 2)]

colnames(trans)
trans <- trans[ , c(5, 1, 2, 3, 4)]

```



## Part 1:  Summary {.tabset}

This part of the report will be directed to your internal team at the consulting
company.  It is intended to document the sources of information that were used 
in the project.  It will also describe the data in less technical terms to team 
members who are not data scientists.  If another member of the team joins the 
project later, they will rely on your descriptions to gain familiarity with the 
data.  To that end, we recommend providing some instructions that will help 
other consultants use the information more effectively.

### Customers

The customers dataset provides information on existing customers that have made
purchases with the store at some point in time. The customer dataset contains 
columns for customer identifier, age, gender--with 2 options: M/F, 
annual income, and region--with 4 options: Midwest/Northeast/South/West. 

```{r customers}
colnames(customers)
levels(customers$region)
summary(customers$region)
levels(customers$gender)
summary(customers$gender)
summary(customers)
str(customers)
missingNo_customers
head(customers, 3)
```


### Products

The products dataset provides information on store-sold products that have been
put up for sale by the store at some point in time. The products dataset 
contains columns for product identifier, category--with 5 options: 
coat/hat/pants/shirt/shoes, and price.

```{r products}
colnames(products)
levels(products$category)
summary(products$category)
summary(products)
str(products)
missingNo_products
head(products, 3)
```


### views

The views datasets (for which we currently have data for month January and
February) cover monthly view information for particular customers. The datasets
include viewing details on time, customer identifier, and product identifier.

```{r views}
colnames(views)
summary(views)
str(views)
missingNo_views
head(views, 3)
```


### transactions

The transactions datasets (for which we currently have data for the currentmost
month), which cover monthly transaction information. The datasets include 
purchase details for each transaction, including time, customer identifier, 
product identifier, price, and quantity.

```{r transactions}
colnames(trans)
summary(trans)
str(trans)
missingNo_trans
head(trans, 3)
```


## Part 2:  Specific Questions {.tabset}

This part of the report will be directed to product managers throughout the 
client's company.  The idea is to give them the useful information they need to 
act on the specific questions they posed.  Plan your communication accordingly.

### Q1

#### Question

During the first week of the month, what were the 10 most viewed products?  Show
the results in a table with the product's identifier, category, and count of the
number of views.

#### Answer

```{r part2_q1}

views.w1 <- views[as.Date(views$time) < w1]

views.w1_category <- merge.data.table(views.w1, products, by = "product_id")
views.w1_category[, c("customer_id", "price") := NULL]

###--------------------------------------------------------------------------###
# Checking the possible factor levels (char string here) we will need to address
###--------------------------------------------------------------------------###
levels(as.factor(products$category))

###--------------------------------------------------------------------------###
# Top 10 views for Each Month Week 1 For Coat Category, Filtering for Coat Cat.
###--------------------------------------------------------------------------###
views.w1.coat <- views.w1_category[views.w1_category$category == 
                                     "coat", .N, keyby = product_id]

###--------------------------------------------------------------------------###
# Re-ordering the entries so they're in "correct" order of Most Viewed To Least
###--------------------------------------------------------------------------###
setorderv(x = views.w1.coat, cols = "N", order = -1)
views.w1_top10.coat <- views.w1.coat[1:10]

print(month)
print("Week 1: Top 10 Coat views")
print.data.frame(views.w1_top10.coat)

###--------------------------------------------------------------------------###
# Top 10 views for Each Month Week 1 For Hat Category, Filtering For Hat Cat.
###--------------------------------------------------------------------------###
views.w1.hat <- views.w1_category[views.w1_category$category == 
                                    "hat", .N, keyby = product_id]

###--------------------------------------------------------------------------###
# Re-ordering the entries so they're in "correct" order of Most Viewed To Least
###--------------------------------------------------------------------------###
setorderv(x = views.w1.hat, cols = "N", order = -1)
views.w1_top10.hat <- views.w1.hat[1:10]

print(month)
print("Week 1: Top 10 Hat views")
print.data.frame(views.w1_top10.hat)

###--------------------------------------------------------------------------###
# Top 10 views for Each Month Week 1 For Pants Category, Filtering For Pants Cat
###--------------------------------------------------------------------------###
views.w1.pants <- views.w1_category[views.w1_category$category == 
                                      "pants", .N, keyby = product_id]

###--------------------------------------------------------------------------###
# Re-ordering the entries so they're in "correct" order of Most Viewed To Least
###--------------------------------------------------------------------------###
setorderv(x = views.w1.pants, cols = "N", order = -1)
views.w1_top10.pants <- views.w1.pants[1:10]

print(month)
print("Week 1: Top 10 Pants views")
print.data.frame(views.w1_top10.pants)

###--------------------------------------------------------------------------###
# Top 10 views for Each Month Week 1 For Shirt Category, Filtering For Shirt Cat
###--------------------------------------------------------------------------###
views.w1.shirt <- views.w1_category[views.w1_category$category == 
                                      "shirt", .N, keyby = product_id]

###--------------------------------------------------------------------------###
# Re-ordering the entries so they're in "correct" order of Most Viewed To Least
###--------------------------------------------------------------------------###
setorderv(x = views.w1.shirt, cols = "N", order = -1)
views.w1_top10.shirt <- views.w1.shirt[1:10]

print(month)
print("Week 1: Top 10 Shirt views")
print.data.frame(views.w1_top10.shirt)

###--------------------------------------------------------------------------###
# Top 10 views for Each Month Week 1 For Shoes Category, Filtering For Shoes Cat
###--------------------------------------------------------------------------###
views.w1.shoes <- views.w1_category[views.w1_category$category 
                                    == "shoes", .N, keyby = product_id]

###--------------------------------------------------------------------------###
# Re-ordering the entries so they're in "correct" order of Most Viewed To Least
###--------------------------------------------------------------------------###
setorderv(x = views.w1.shoes, cols = "N", order = -1)
views.w1_top10.shoes <- views.w1.shoes[1:10]

print(month)
print("Week 1: Top 10 Shoes views")
print.data.frame(views.w1_top10.shoes)

```

### Q2

#### Question

During the whole month, what were the 10 most viewed products for each category?
Show the results in separate tables by category.  Including only the product's 
identifier and the count of the number of views.


#### Answer {.tabset}

```{r part2_q2_overall_calculations}

###--------------------------------------------------------------------------###
# Data table manipulation to merge DT/DFs, create/remove columns based on values
###--------------------------------------------------------------------------###
views.category <- merge.data.table(views, products, by = "product_id")
views.category[, c("customer_id", "price") := NULL]

```

##### Shirt

```{r part2_q2_shirt}

###--------------------------------------------------------------------------###
# Top 10 views for Each Month For Shirt Category
###--------------------------------------------------------------------------###
views.shirt <- views.category[views.category$category 
                              == "shirt", .N, keyby = product_id]

###--------------------------------------------------------------------------###
# Re-ordering the entries so they're in "correct" order of Most Viewed To Least
###--------------------------------------------------------------------------###
setorderv(x = views.shirt, cols = "N", order = -1)
views.top10.shirt <- views.shirt[1:10]

print(month)
print("Top 10 Shirt views")
print.data.frame(views.top10.shirt)

```

##### Pants

```{r part2_q2_pants}

###--------------------------------------------------------------------------###
# Top 10 views for Each Month For Pants Category
###--------------------------------------------------------------------------###
views.pants <- views.category[views.category$category ==
                                "pants", .N, keyby = product_id]

###--------------------------------------------------------------------------###
# Re-ordering the entries so they're in "correct" order of Most Viewed To Least
###--------------------------------------------------------------------------###
setorderv(x = views.pants, cols = "N", order = -1)
views.top10.pants <- views.pants[1:10]

print(month)
print("Top 10 Pants views")
print.data.frame(views.top10.pants)

```

##### Coat

```{r part2_q2_coat}

###--------------------------------------------------------------------------###
# Top 10 views for Each Month For Coat Category
###--------------------------------------------------------------------------###
views.coat <- views.category[views.category$category == 
                               "coat", .N, keyby = product_id]

###--------------------------------------------------------------------------###
# Re-ordering the entries so they're in "correct" order of Most Viewed To Least
###--------------------------------------------------------------------------###
setorderv(x = views.coat, cols = "N", order = -1)
views.top10.coat <- views.coat[1:10]

print(month)
print("Top 10 Coat views")
print.data.frame(views.top10.coat)

```

##### Shoes

```{r part2_q2_shoes}

###--------------------------------------------------------------------------###
# Top 10 views for Each Month For Shoes Category
###--------------------------------------------------------------------------###
views.shoes <- views.category[views.category$category 
                              == "shoes", .N, keyby = product_id]

###--------------------------------------------------------------------------###
# Re-ordering the entries so they're in "correct" order of Most Viewed To Least
###--------------------------------------------------------------------------###
setorderv(x = views.shoes, cols = "N", order = -1)
views.top10.shoes <- views.shoes[1:10]

print(month)
print("Top 10 Shoes views")
print.data.frame(views.top10.shoes)

```

##### Hat

```{r part2_q2_hat}

###--------------------------------------------------------------------------###
# Top 10 views for Each Month For Hat Category
###--------------------------------------------------------------------------###
views.hat <- views.category[views.category$category
                            == "hat", .N, keyby = product_id]

###--------------------------------------------------------------------------###
# Re-ordering the entries so they're in "correct" order of Most Viewed To Least
###--------------------------------------------------------------------------###
setorderv(x = views.hat, cols = "N", order = -1)
views.top10.hat <- views.hat[1:10]

print(month)
print("Top 10 Hat views")
print.data.frame(views.top10.hat)

```


### Q3

#### Question

What was the total revenue for each category of product during the month?  Show 
the results in a single table sorted in decreasing order.

#### Answer

```{r part2_q3}

###--------------------------------------------------------------------------###
# Data table manipulation to merge DT/DFs, create/remove columns based on values
###--------------------------------------------------------------------------###
trans.category <- merge.data.table(trans, products, by = "product_id")
trans.category[, total := price.x * quantity]
trans.category[, c("time", "customer_id", "quantity", 
                       "price.x", "price.y") := NULL]

revs <- trans.category[,lapply(.SD, sum, na.rm = TRUE), 
                       by = "category", .SDcols = c("total")]

###--------------------------------------------------------------------------###
# Re-ordering the entries so they're in "correct" order of Most Viewed To Least
###--------------------------------------------------------------------------###
setorderv(x = revs, cols = "total", order = -1)

print(month)
print("Revenue Per Category")
print.data.frame(revs)

```

### Q4

#### Question

Among customers with at least one transaction, show the average, median, and 
standard deviation of the customers' monthly spending on the site.

#### Answer

```{r part2_q4}

###--------------------------------------------------------------------------###
# Data table manipulation to merge DT/DFs, create/remove columns based on values
###--------------------------------------------------------------------------###
customer_trans <- merge.data.table(customers, trans, 
                                        by = "customer_id")

customer_trans[, total := price * quantity]
customer_trans[, c("age", "gender", "income", "region", "time", "price", 
                        "quantity", "product_id") := NULL]

customer_totals <- customer_trans[, `:=`(average = mean(total), 
                       median = median(total), standard_deviation = sd(total)),
                       by = customer_id]

summary(customer_totals)
summary(customer_totals$total)

```

### Q5

#### Question

What is the percentage distribution of spending by gender?  Show the amount of 
revenue and the percentage.

#### Answer

```{r part2_q5}

###--------------------------------------------------------------------------###
# Data table manipulation to merge DT/DFs, create/remove columns based on values
###--------------------------------------------------------------------------###
totals <- trans[, total := price * quantity]
totals <- totals[, c("time", "product_id", "price", "quantity") := NULL]

total_gen <- merge.data.table(totals, customers, by = "customer_id")                     
total_gen <- total_gen[, c("age", "income", "region") := NULL]

gen_totals <- gen_totals[, c("customer_id") := NULL]

overall_revenue <- sum(gen_totals$total)

gen_totals <- gen_totals[,lapply(.SD, sum, na.rm = TRUE), 
                         by = "gender", .SDcols = c("total")]

gen_totals <- gen_totals[, `:=`(overall_revenue = overall_revenue, 
                      percentage = (sum(total)/overall_revenue)), by = gender]

print.data.frame(gen_totals)

```

### Q6

#### Question

Using linear regression, what is the effect of an extra ten thousand dollars of 
income on monthly spending for a customer while adjusting for age, gender, and 
region?

#### Answer

```{r part2_q6}

###--------------------------------------------------------------------------###
# Data table manipulation to merge DT/DFs, create/remove columns based on values
###--------------------------------------------------------------------------###
customer_trans <- merge.data.table(customers, trans, by = "customer_id")

customer_trans <- customer_trans[ , `:=`(inflated_income = income + 10000), 
                                  by = "customer_id"]


###--------------------------------------------------------------------------###
# Equation for lm regression calculation, utilizing Prof. Shilane's coeff. f(x)
###--------------------------------------------------------------------------###
customer_trans[, show.coef(mod.lm = lm(formula = total ~ age + gender + region 
              + inflated_income, data = customer_trans)), by = "customer_id"]

```


### Q7

#### Question

Among customers who viewed at least 1 product, how many had at least one 
purchase during the month?  Show the total number and as a percentage of the 
users with a view.

#### Answer

```{r part2_q7}

###--------------------------------------------------------------------------###
# Pulling unique customer_id values to compare with one another for calculations
###--------------------------------------------------------------------------###
unique_tran <- unique(trans$customer_id)
unique_view <- unique(views$customer_id)

vt_cust <- which(unique_tran %in% unique_view)
vt_cust <- unique_tran[vt_cust]

length(vt_cust)
length(vt_cust)/length(unique_view)

```

### Q8

#### Question

Now let's look at the viewing habits in different age groups, including 18-34, 
35-49, 50-64, and 65+.  Within each group, what were the mean, median, and 
standard deviation for the number of unique products viewed per customer?

#### Answer

```{r part2_q8}

cust_views <- merge.data.table(views, customers, by = "customer_id")
cust_views <- cust_views[, 
                  c("time", "gender", "income", "region") := NULL]

cust_views <- cust_views[, .(num_items = length(unique(product_id))), 
                  by = c("customer_id", "age")]

age1_views <- cust_views[age < 35]
summary(age1_views$num_items)
sd(age1_views$num_items)

age2_views <- cust_views[(age > 34 & age < 50)]
summary(age2_views$num_items)
sd(age2_views$num_items)

age3_views <- cust_views[(age > 49 & age < 65)]
summary(age3_views$num_items)
sd(age3_views$num_items)

age4_views <- cust_views[age > 64]
summary(age4_views$num_items)
sd(age4_views$num_items)

```


### Q9 

#### Question

What is the correlation between a user's total page views and total spending?  
For customers without a transaction, include their spending as zero.

#### Answer

```{r part2_q9}

###--------------------------------------------------------------------------###
# Data table manipulation to merge DT/DFs, create/remove columns based on values
###--------------------------------------------------------------------------###
customer_id <- unique(views$customer_id);

i <- 1;
j <- 1;
k <- length(cust_views);
cust_count <- c(length = j);

while(i < (k+1)){
    cust_count[j] <- sum(views[customer_id == customer_id[j], which = TRUE])
    i = i + 1
    j = j + 1
}

cust_count <- round_numerics(cust_count, 1)
cust_view_cts <- data.table(customer_id, cust_count)

spend_totals <- trans[, .(spend_total = sum(total)), by = "customer_id"]
total_Ds <- merge.data.table(cust_view_cts, spend_totals, by = "customer_id")
total_Ds$cust_count <- round_numerics(total_Ds$cust_count, 1)

zSpend <- !(cust_view_cts$customer %in% total_Ds$customer_id)
total_Zs <- cust_view_cts[zSpend]

total_Zs$cust_count <- round_numerics(total_Zs$cust_count, 1)
total_Zs[,`:=`(spend_total = 0),]

list_tals <- list(total_Ds, total_Zs)
cust_tals <- rbindlist(list_tals, use.names = TRUE, fill = FALSE)

summary(cust_tals)
cor(cust_tals$cust_count, cust_tals$spend_total)

```

### Q10

#### Question

Which customer purchased the largest number of coats?  In the event of a tie, 
include all of the users who reached this value.  Show their identifiers and 
total volume.

#### Answer

```{r part2_q10}

###--------------------------------------------------------------------------###
# Data table manipulation to merge DT/DFs, create/remove columns based on values
###--------------------------------------------------------------------------###
coats <- products[products$category == "coat"]
coats <- coats[ , c("price") := NULL]

trans <- fread(current_trans_data)
trans <- trans[ , c("price", "time") := NULL]

coat_trans <- merge.data.table(coats, trans, keyby = "product_id")
coat_trans[ , c("product_id", "category") := NULL]
coat_totes <- coat_trans[, `:=`(total = quantity, customer = customer_id), 
                         by = eval(unique("customer_id"))]
coat_totes <- coat_totes[,c("total", "customer") := NULL]

###--------------------------------------------------------------------------###
# Re-ordering the entries so they're in "correct" order of Most Viewed To Least
###--------------------------------------------------------------------------###
setorderv(x = coat_totes, cols = "quantity", order = -1)
head(coat_totes, 10)

print("MONTH")
print("Top Coat Sales")
print.data.frame(coat_totes)

```

