---
title: 'Mobile Phones'
output: flexdashboard::flex_dashboard
runtime: shiny
---


```{r setup, include = FALSE}
library(shiny);
library(Hmisc);
library(knitr);

library(rmarkdown);
library(flexdashboard);

library(tidyverse);
library(formulaic);

library(DT);
library(data.table);

assignInNamespace('cedta.override', c(data.table:::cedta.override,'rmarkdown'), 'data.table')

opts_chunk$set(echo = FALSE, comment='', warning = FALSE, message = FALSE, tidy.opts=list(width.cutoff=55), tidy = TRUE)

setwd("~/Desktop/5902/IP3/Reports")
```

```{r read_data}
cellphones <- fread('../Data/mobile phone survey data.csv', verbose = F);
```

```{r source_functions}
source('constants.R');
source('functions.R');
```

```{r constants}
# Most constants have been placed in the file constants.R to unify reporting and
# application work. Additional functions unique to reporting engine added here.

# Constant for id Var
idVal <- 'id';

# Constants for Respondent Vars
ageVal <- 'Age';
genderVal <- 'Gender';
incomeVal <- 'Income';
regionVal <- 'Region';
personaVal <- 'Persona';

# Constant for Product Var
productVal <- 'Product';

# Constants for Engagement Vars
awarenessVal <- 'Awareness';
considerationVal <- 'Consideration';
consumptionVal <- 'Consumption';
satisfactionVal <- 'Satisfaction';
advocacyVal <- 'Advocacy';

# Creating Group Values for Age & Income (which still need to be spliced)
ageGroupVal <- 'ageGroups';
incomeGroupVal <- 'incomeGroups';

# Creating Spliced Factor Levels for Group Vars for Age & Income
cellphones$ageGroups <- cut(cellphones$Age, breaks = c(17, 34, 49, 64, Inf, 
  right = FALSE), labels = c('< 17 years old', '18-34 years old', '35-49 years 
  old', '50-64 years old', '65+ years old'));
cellphones$incomeGroups <- cut(cellphones$Income, breaks = c(0, 49999, 74999, 
  99999, 149999, Inf), labels = c('<$50,000', '$50,000 - <$75,000', '$75,000 - 
    <$100,000', '$100,000 - <$150,000', '$150,000+'));

# Ensuring Factor Levels are Unique For All Vars
ageGroups <- cellphones[ , sort(unique(get(ageGroupVal)))];
genderGroups <- cellphones[ , sort(unique(get(genderVal)))];
incomeGroups <- cellphones[ , sort(unique(get(incomeGroupVal)))];
regionGroups <- cellphones[ , sort(unique(get(regionVal)))];
personaGroups <- cellphones[ , sort(unique(get(personaVal)))];

# Ensuring Factor Levels i.e. Brands are Unique for All Product Vars
productVal <- cellphones[ , unique(get(productVal))];

# Constants for BP Vars
userFriendlyBP <- 'BP_User_Friendly_0_10';
fastBP <- 'BP_Fast_0_10';
batteryLifeBP <- 'BP_Battery_Life_0_10';
cameraBP <- 'BP_Camera_0_10';
sleekBP <- 'BP_Sleek_0_10';
stylishBP <- 'BP_Stylish_0_10';
statusSymbolBP <- 'BP_Status_Symbol_0_10';
goodScreenSizeBP <- 'BP_Good_Screen_Size_0_10';
boringBP <- 'BP_Boring_0_10';
bulkyBP <- 'BP_Bulky_0_10';
fragileBP <- 'BP_Fragile_0_10';
expensiveBP <- 'BP_Expensive_0_10';

# Constants for Product(Brand) Vars
AllButtons <- 'All Buttons';
AppMap <- 'App Map';
Buzzdial <- 'Buzzdial';
Cellularity <- 'Cellularity';
CommunicNation <- 'Communic Nation';
MaybeMobile <-  'Maybe Mobile';
MobileMayhem <- 'Mobile Mayhem';
MobilitEE <- 'MobilitEE';
Mobzilla <- 'Mobzilla';
NextText <- 'Next Text';
NoButtons <- 'No Buttons';
OfftheHook <- 'Off the Hook';
Phonatics <- 'Phonatics';
PhoneZone <- 'PhoneZone';
PocketDialz <- 'PocketDialz';
RingRing <- 'RingRing';
Screenz <- 'Screenz';
Smartophonic <- 'Smartophonic';
SpeedDials <- 'SpeedDials';
Triumphone <- 'Triumphone';
```

```{r variables}
# Respondent Variables, Describe Customer Demographics and Behavioral Traits
resVars <- c(ageGroupVal, genderVal, incomeGroupVal, regionVal, personaVal);

# Engagement Variables, Cover Various Means of Ascertaining Customer Opinion
engVars <- c(awarenessVal, considerationVal, consumptionVal, satisfactionVal,
  advocacyVal);

# Brand Perception Variables (BP), Contain User Feedback/Ratings On Topics
bpVars <- c(userFriendlyBP, fastBP, batteryLifeBP, cameraBP, sleekBP, stylishBP, 
  statusSymbolBP, goodScreenSizeBP, boringBP, bulkyBP, fragileBP, expensiveBP);

# Product Variables (The Different Brand / Product Types of Cell Phones)
prodVars <- c(AllButtons, AppMap, Buzzdial, Cellularity, CommunicNation,
  MaybeMobile, MobileMayhem, MobilitEE, Mobzilla, NextText, NoButtons, 
  OfftheHook, Phonatics, PhoneZone, PocketDialz, RingRing, Screenz, Smartophonic,
  SpeedDials, Triumphone)
```

```{r functions}
# Most functions have been placed in the file functions.R to unify reporting and
# application work. Additional functions unique to reporting engine added here.

ovDiff <- function(q4_1, ovEngVar1, ovEngVar2){

  if(ovEngVar1 == 'Awareness'){

    if(ovEngVar2 == 'Consideration'){
      ovDiff <- abs(q4_1$Awareness - q4_1$Consideration)
    }

    else if(ovEngVar2 == 'Consumption'){
      ovDiff <- abs(q4_1$Awareness - q4_1$Consumption)
    }

    else if(ovEngVar2 == 'Satisfaction'){
      ovDiff <- abs(q4_1$Awareness - q4_1$Satisfaction)
    }

    else if(ovEngVar2 == 'Advocacy'){
      ovDiff <- abs(q4_1$Awareness - q4_1$Advocacy)
    }

  }

  else if(ovEngVar1 == 'Consideration'){

    if(ovEngVar2 == 'Consumption'){
      ovDiff = abs(q4_1$Consideration - q4_1$Consumption)
    }

    else if(ovEngVar2 == 'Satisfaction'){
      ovDiff = abs(q4_1$Consideration - q4_1$Satisfaction)
    }

    else if(ovEngVar2 == 'Advocacy'){
      ovDiff= abs(q4_1$Consideration - q4_1$Advocacy)
    }

  }

  else if(ovEngVar1 == 'Consumption'){

    if(ovEngVar2 == 'Satisfaction'){
      ovDiff = abs(q4_1$Consumption - q4_1$Satisfaction)
    }

    else if(ovEngVar2 == 'Advocacy'){
      ovDiff = abs(q4_1$Consumption - q4_1$Advocacy)
    }

  }

  else if(ovEngVar1 == 'Satisfaction'){

    if(ovEngVar2 == 'Advocacy'){
      ovDiff = abs(q4_1$Satisfaction - q4_1$Advocacy)
    }

  }

  else if((ovEngVar1 == 'Awareness' & ovEngVar2 == 'Awareness') |
          (ovEngVar1 == 'Consideration' & ovEngVar2 == 'Consideration' ) |
          (ovEngVar1 == 'Consumption' & ovEngVar2 == 'Consumption') |
          (ovEngVar1 == 'Satisfaction' & ovEngVar2 == 'Satisfaction') |
          (ovEngVar1 == 'Advocacy' & ovEngVar2 == 'Advocacy' )){

    ovDiff <- 0

  }

  ovDiffs <- ovDiff

  return(ovDiffs)

}

###--------------------------------------------------------------------------###
# Function: Prof. David Shilane, Lecture 04, APAN S5902, Columbia University SPS
###--------------------------------------------------------------------------###

round_numerics <- function(x, digits = 2){
  
    if (is.numeric(x)) {
        x <- round(x = x, digits = digits)
    }
    return(x)
}
###--------------------------------------------------------------------------###
# Function: Haotian Yue, APAN S5902, Columbia University SPS (Current Student)
###--------------------------------------------------------------------------###

round_table <- function(values, digits = 2){
  
    tabled_values <- table(values);
    percents <- 100 * tabled_values/(sum(tabled_values));
    rounded_table <- round_numerics(x = percents, digits = digits);
    
    return(rounded_table)
    
}
###--------------------------------------------------------------------------###
# Function: Haotian Yue, APAN S5902, Columbia University SPS (Current Student)
###--------------------------------------------------------------------------###

engage <- function(values, output_values, input_values, model_type){
  
  eng <- fit(values = values, output_values = output_values, 
    input_values = input_values, model_type = model_type);
  
  return(eng);
}
###--------------------------------------------------------------------------###
# Function: Haotian Yue, APAN S5902, Columbia University SPS (Current Student)
###--------------------------------------------------------------------------###

fit <- function(values, output_values, input_values, model_type, digits = 3){
  
  final_formula <- create.formula(outcome.name = output_values,  input.names =
    input_values, dat = data, reduce = TRUE);
  
  if(model_type == 'logistic'){
    mod <- glm(formula = final_formula, family = 'binomial', values = data);
    mod_summary <- logistic_regression_summary(glm_mod = mod, digits = digits);
  }
  
  if(model_type == 'linear'){
    mod <- lm(formula = final_formula, values = data);
    mod_summary <- linear_regression_summary(lm_mod = mod, digits = digits);
  }

  mod_summary_rounded <- mod_summary[, lapply(X = .SD, FUN = 'round_numerics', 
    digits = digits)];
  
  return(mod_summary_rounded);
  
}
###--------------------------------------------------------------------------###
# Function: Haotian Yue, APAN S5902, Columbia University SPS (Current Student)
###--------------------------------------------------------------------------###

logistic_regression_summary <- function(glm_mod, digits = 3, alpha = 0.05){
  
  glm_coefs <- as.data.table(summary(glm_mod)$coefficients, keep.rownames = TRUE);
  setnames(x = glm_coefs, old = 'rn', new = 'Variable');
  z <- qnorm(p = 1-alpha/2, mean = 0, sd = 1);
  glm_coefs[, Odds.Ratio := exp(Estimate)];
  glm_coefs[, OR.Lower.95 := exp(Estimate - z * `Std. Error`)];
  glm_coefs[, OR.Upper.95 := exp(Estimate + z * `Std. Error`)];
  
  return(glm_coefs[])
  
}
###--------------------------------------------------------------------------###
# Function: Haotian Yue, APAN S5902, Columbia University SPS (Current Student)
###--------------------------------------------------------------------------###

linear_regression_summary <- function(lm_mod, digits = 3, alpha = 0.05){
  
  lm_coefs <- as.data.table(summary(lm_mod)$coefficients, keep.rownames = TRUE);
  setnames(x = lm_coefs, old = 'rn', new = 'Variable');

  z <- qnorm(p = 1 - alpha/2, mean = 0, sd = 1);
  
  lm_coefs[, Coef.Lower.95 := Estimate - z * `Std. Error`];
  lm_coefs[, Coef.Upper.95 := Estimate + z * `Std. Error`];
  
  return(lm_coefs)
  
}
###--------------------------------------------------------------------------###
# Function: Haotian Yue, APAN S5902, Columbia University SPS (Current Student)
###--------------------------------------------------------------------------###

agg <- function(agg){
  
  mean_agg <- mean(get(input$aeEngState)[-agg],na.rm = TRUE);
  
  return(mean_agg)
  
}
```

Introduction
=====================================  

Hello,

Please find the following Dynamic Reporting Engine tool for your convenience.
You will find that you can pull up the data for various questions and variables.

Thank you,

C. Blanchard
chb2132

1|Respondent Variables
===================================

Row {data-height=500}
-------------------------------------
```{r q1_input}
inputPanel(
  selectInput(inputId = 'resVar', label = 'Respondent Variable:', choices = 
                resVars, selected = NULL, multiple = FALSE, selectize = TRUE)
)
```

Row {data-height=500}
-------------------------------------

```{r q1_output}

cellphones <- fread('../Data/mobile phone survey data.csv', verbose = F);

renderPlot({
  
  q1_0 <- round_table(values = cellphones[get(productVal) == get(productVal)[1],
    get(input$resVar)]);
  
  barplot(height = q1_0, space = 0.01, las = 1, main = input$resVar, ylab = 
    'Percentages', xlab = input$resVar, ylim = c(0, 1.2 * max(q1_0, na.rm = TRUE)))
  
    space_val = 0
    
    text(x = -0.3 + 1:length(q1_0) * (1 + space_val), y = q1_0, labels = 
      sprintf('%.1f%%', q1_0), pos = 2)
})
```

2|Segmented Outcomes
=====================================  


Row {data-height=500}
-------------------------------------

```{r q2_input}
inputPanel(
  
  selectInput(inputId = 'soEngState', label = 'Engagement:', choices = 
    engVars, selected = NULL, multiple = FALSE, selectize = TRUE),
    
  selectInput(inputId = 'soAgeGroups', label = 'Age Groups:', choices = 
    ageGroups, selected = NULL, multiple = TRUE, selectize = TRUE),
    
  selectInput(inputId = 'soGenderGroups', label = 'Gender Groups:', choices = 
    genderGroups, selected = NULL, multiple = TRUE, selectize = TRUE),
    
  selectInput(inputId = 'soIncomeGroups', label = 'Income Groups:', choices = 
    incomeGroups, selected = NULL, multiple = TRUE, selectize = TRUE),
    
  selectInput(inputId = 'soRegionGroups', label = 'Region Groups:', choices = 
    regionGroups, selected = NULL, multiple = TRUE, selectize = TRUE),
    
  selectInput(inputId = 'soPersonaGroups', label = 'Persona Groups:', choices = 
    personaGroups, selected = NULL, multiple = TRUE, selectize = TRUE),
  
  sliderInput(inputId = 'top_N', label = 'Top N Products:', min = 1, max = 20, 
    value = 10, step = 1, round = FALSE, ticks = TRUE, animate = FALSE)
)
```

Row {data-height=500}
-------------------------------------

```{r q2_output}
cellphones <- fread('../Data/mobile phone survey data.csv', verbose = F);

renderDT({
  
  q2_0 <- cellphones[get(ageGroup) %in% input$soAgeGroups & get(genderGroups) 
    %in% input$soGenderGroups & get(incomeGroupVal) %in% input$soIncomeGroups & 
    get(regionGroups) %in% input$soRegionGroups & get(personaGroups) %in% 
    input$soPersonaGroups];
  
  q2_1 <- q2_0[,.(Avg = mean(x = get(input$soEngState), na.rm = TRUE) * 100),
    by = 'Product'];
  
  q2_1 %>% head(input$top_N);
  
})

renderPlot({
  
  outcomeRates <- cellphones[, .(Avg = 100 * mean(get(input$eng_state), 
    na.rm = TRUE) / max(get(input$eng_state), na.rm = TRUE)), by = 'Product']

  barplot(height = outcomeRates, names.arg = outcomeRates,
    main = input$eng_state, ylab = sprintf('Rate of %s', input$eng_state), ylim 
    = c(-100, 120), xaxt = 'n', axes = FALSE)
  
  axis(side = 2, at = 20 * (0:5), las = 2)
  
  text(x = -0.5 + 1.02 * 1:outcomeRates[.N], y = -15, labels = 
    outcomeRates[get(productVal)], srt = 45, pos = 2)

  space_val = 0
  
  text(x = -0.4 + 1:outcomeRates[.N] * (1 + space_val), y = outcomeRates[Avg], 
    labels = sprintf('%.1f%%', outcomeRates[Avg]), pos = 3)
  
})
```

3|Overall Brand Perceptions
=====================================  

Row {data-height=500}
-------------------------------------

```{r q3_input}
inputPanel(
  
  selectInput(inputId = 'bpAgeGroups', label = 'Age Groups:', choices = 
    ageGroups, selected = NULL, multiple = TRUE, selectize = TRUE),
  
  selectInput(inputId = 'bpGenderGroups', label = 'Gender Groups:', choices = 
    genderGroups, selected = NULL, multiple = TRUE, selectize = TRUE),
  
  selectInput(inputId = 'bpIncomeGroups', label = 'Income Groups:', choices = 
    incomeGroups, selected = NULL, multiple = TRUE, selectize = TRUE),
  
  selectInput(inputId = 'bpRegionGroups', label = 'Region Groups:', choices = 
    regionGroups, selected = NULL, multiple = TRUE, selectize = TRUE),
  
  selectInput(inputId = 'bpPersonaGroups', label = 'Persona Groups:', choices = 
    personaGroups,selected = NULL, multiple = TRUE, selectize = TRUE),
  
  # Are we supposed to be aggregating this Brand Perception beforehand and 
  # providing for the specific chosen subsets of bp variables selected and 
  # subgroups within each?
  
  selectInput(inputId = 'bpVarsChoice', label = 'Brand Perception Variables:', 
    choices = bpVars, selected = NULL, multiple = FALSE, selectize = TRUE),
  
  sliderInput(inputId = 'top_N', label = 'No. Products:', min = 1, max = 20, 
        value = 10, step = 1)
)
```

Row {data-height=500}
-------------------------------------

```{r q3_output}
cellphones <- fread('../Data/mobile phone survey data.csv', verbose = F);

renderDT({
  
  q3_0 = cellphones[get(ageGroupVal) %in% input$bpAgeGroups & get(genderGroups)
    %in% input$bpGenderGroups & get(incomeGroupVal) %in% input$bpIncomeGroups & 
    get(regionGroups) %in% input$bpRegionGroups & get(personaGroups) %in% 
    input$bpPersonaGroups];

  q3_0 <- cellphones[,lapply(.SD, mean, na.rm = TRUE), by = 'Product', 
    .SDcols = c(names(cellphones)[9:20])]

  # Correcting BP Values According to Given Equation for Negative BP Traits/Vars
  
  q3_1 <- q3_0
  
  q3_1$boringBP <- 10 - q3_1$boringBP
  q3_1$bulkyBP <- 10 - q3_1$bulkyBP
  q3_1$fragileBP <- 10 - q3_1$fragileBP
  q3_1$expensiveBP <- 10 - q3_1$expensiveBP
  
  q3_2 <- data.table(Brand = q3_1$Product, Perception = rowMeans(q3_1[ , 2:13]))
  
  q3_2 <- q3_2[order(-Perception)]
  
  q3_2 %>% head(input$top_N)

})

renderPlot({
  
  q3_table <- round_table(values = cellphones[, input$bpVarsChoice,
                                              get(productVal)])
  
  barplot(height = q3_table, space= 0.01, las = 1, ylab = 'Overall Brand Perception', 
    xlab = input$bpVarsChoice, ylim = c(0, 1.2 * max(q3_table[mean], na.rm = 
    TRUE)))
  
    text(x = -0.4 + 1:length(q3_table), y = q3_table, labels = 
      sprintf('%.1f%%', q3_table), pos = 3)
})
```

4|Gaps in Outcomes
=====================================  

Row {data-height=500}
-------------------------------------

```{r q4_input}

inputPanel(

  checkboxInput(inputId = 'goShowPercent', label = 'Show/Hide %s:', value = FALSE),
    
  sliderInput(inputId = 'top_N', label = 'No. Products:', min = 1, max = 20, 
              value = 10, step = 1, round = FALSE, animate = FALSE),
  
  sliderInput(inputId = "Digits", label = "No. Digits", min = 1, max = 10, 
    value = 5, step = 1, round = FALSE, animate = FALSE),
  
  selectInput(inputId = 'ovEngVar1', label = 'First Outcome Variable:', choices = 
    engVars, selected = 'Awareness', multiple = FALSE, selectize = TRUE),
  
  selectInput(inputId = 'ovEngVar2', label = 'Second Outcome Variable:', choices = 
    engVars, selected = 'Consumption', multiple = FALSE, selectize = TRUE)
  
)
```

Row {data-height=500}
-------------------------------------

```{r q4_output}

renderDT({
  
  cellphones <- fread('../Data/mobile phone survey data.csv', verbose = F);
  
  q4_0 <- cellphones[, c(7:8, 21:24)];
  
  q4_1 <- q4_0[, .(Awareness = mean(x = Awareness, na.rm = TRUE) * 100, Consideration = mean(x = Consideration, na.rm = TRUE) * 100,
    Consumption = mean(x = Consumption, na.rm = TRUE) * 100, Satisfaction = mean(x = Satisfaction, na.rm = TRUE) * 10, Advocacy = 
    mean(x = Advocacy, na.rm = TRUE) * 100), by = 'Product'];
  
  ovEngVar1 <- input$ovEngVar1
  ovEngVar2 <- input$ovEngVar2
  
  q4_1$ovDiff <- ovDiff(q4_1 = q4_1, ovEngVar1 = ovEngVar1, ovEngVar2 = ovEngVar2)
  q4_1$ovDiff <- round_numerics(x = q4_1$ovDiff, input$Digits)
  
  q4_1 <- q4_1[, c('Awareness', 'Consideration', 'Consumption', 'Satisfaction', 
    'Advocacy') := NULL][order(-ovDiff)]
  
  q4_vect <- as.vector(as.numeric(q4_1$ovDiff))
  
  if (input$goShowPercent == TRUE){
    q4_1$ovDiff <- paste(q4_1$ovDiff, '%', sep = '')
  }
  
  colnames(q4_1) <- c('Product', 'OV Difference')
  
  q4_1 %>% head(input$top_N)
  
})
  
renderPlot({
  
  cellphones <- fread('../Data/mobile phone survey data.csv', verbose = F);
  
  q4_0 <- cellphones[, c(7:8, 21:24)];
  
  q4_1 <- q4_0[, .(Awareness = mean(x = Awareness, na.rm = TRUE) * 100, Consideration = mean(x = Consideration, na.rm = TRUE) * 100,
    Consumption = mean(x = Consumption, na.rm = TRUE) * 100, Satisfaction = mean(x = Satisfaction, na.rm = TRUE) * 10, Advocacy = 
    mean(x = Advocacy, na.rm = TRUE) * 100), by = 'Product'];
  
  ovEngVar1 <- input$ovEngVar1
  ovEngVar2 <- input$ovEngVar2
  
  q4_1$ovDiff <- ovDiff(q4_1 = q4_1, ovEngVar1 = ovEngVar1, ovEngVar2 = ovEngVar2)
  q4_1$ovDiff <- round_numerics(x = q4_1$ovDiff, input$Digits)
  
  q4_1 <- q4_1[, c('Awareness', 'Consideration', 'Consumption', 'Satisfaction', 
    'Advocacy') := NULL][order(-ovDiff)]
  
  #q4_table <- datatable(q4_1, rownames = FALSE)
  #colnames(q4_table) <- c('Product', 'ovDiff')
  
  if (input$goShowPercent == TRUE){
    q4_1$ovDiff <- paste(q4_1$ovDiff, '%', sep = '')
  }
  
  colnames(q4_1) <- c('Product', 'OV Difference')
  
  q4_1 <- q4_1 %>% head(input$top_N)
  
  barplot(height = q4_1, names.arg = productVal, main = sprintf('%s vs. %s', 
    ovEngVar1, ovEngVar2), ylim = c(0, 1.2 * max(q4_1, na.rm = TRUE)),
    ylab)
  
  #if(input$goShowPercent == TRUE){
  #  space_val = 0
  #  text(x = length(q4_1), y = q4_1, labels = sprintf('%.1f%%', q4_1), pos = 3)
  #}

})
```

5|Aggregated Engagement
=====================================  

Row {data-height=500}
-------------------------------------

```{r q5_input}

inputPanel(
  
  selectInput(inputId = 'aeEngState', label = 'State of Engagement:', choices =
   engVars, selected = NULL, multiple = FALSE, selectize = TRUE),
    
  selectInput(inputId = 'aeProdChoice', label = 'Product(s):', choices = prodVars, 
    selected = NULL, multiple = TRUE, selectize = TRUE),
    
  selectInput(inputId = 'aeAddVars', label = 'Additional Variables:', choices = 
    resVars, selected = NULL, multiple = TRUE, selectize = TRUE),
    
  selectInput(inputId = 'aeAgeGroup', label = 'Age Groups:', choices = 
    ageGroups, selected = NULL, multiple = TRUE, selectize = TRUE),
    
  selectInput(inputId = 'aeGenderGroup', label = 'Gender Groups:', 
    choices = genderGroups, selected = NULL, multiple = TRUE, selectize = TRUE),
    
  selectInput(inputId = 'aeIncomeGroup', label = 'Income Groups:', 
    choices = incomeGroups, selected = NULL, multiple = TRUE, selectize = TRUE),
    
  selectInput(inputId = 'aeRegionGroup', label = 'Region Groups:', 
    choices = regionGroups, selected = NULL, multiple = TRUE, selectize = TRUE),
    
  selectInput(inputId = 'aePersonaGroup', label = 'Persona Groups:', 
    choices = personaGroups, selected = NULL, multiple = TRUE, selectize = TRUE)
  
)
```

Row {data-height=500}
-------------------------------------

```{r q5_output}
cellphones <- fread('../Data/mobile phone survey data.csv', verbose = F);

renderDT({
  
  q5_0 = cellphones[, aggEng := sapply(seq_along(input$aeEngState), function(agg)
    mean(input$aeEngState)[-agg]), by = list(id)];
  
  q5_0[is.na(q5_0)] = 0;
  
  q5_0$aggEng = round_numerics(x = q5_0$aggEng, digits = 4)
  
  q5_1 <- q5_0[get(productVal) %in% input$aeProdChoice & get(ageVal) %in% 
      input$aeAgeGroup & get(genderVal) %in% input$aeGenderGroup & 
      get(incomeVal) %in% input$aeIncomeGroup & get(regionVal) %in% 
      input$aeRegionGroup & get(personaVal) %in% input$aePersonaGroup];
  
  if(input$aeEngState == satisfactionVal){
    model <- 'linear'
    dynamic_table = c('Variable','Estimate','Coef.Lower.95',
      'Coef.Upper.95','Pr(>|t|)')
  }
   
  if(input$aeEngState != satisfactionVal){
    model <- 'logistic'
    dynamic_table = c('Variable','Odds.Ratio','OR.Lower.95',
      'OR.Upper.95','Pr(>|z|)')
   }
   
  q5_table <- fit(values = q5_1, output_values = input$aeEngState, input_values = 
    input$aeAddVars, model_type = model)
   
  q5_table <- datatable(q5_table);
   
  q5_table %>% select(dynamic_table);
   
})
```
